Non-word repetition in Yélî Dnye

### 2021-10-13 manuscript.Rmd
add indiv scores to model pred plot

plot_model(xl_fr,type="pred",terms=c("age.rounded_s","avg_fr_s"))
```

<!-- ac2mc if it's easy for you to add dots representing actual children in the above, that would be awesome! If not, I can try to tackle it :) -->

>>>>

trnsc.inc.indivs <- trnsc.inc %>%
  mutate(avg_fr_s = case_when(
    avg_fr_s <= mean(xl_fr_tab$xlf)-sd(xl_fr_tab$xlf) ~ -1,
    avg_fr_s >= mean(xl_fr_tab$xlf)+sd(xl_fr_tab$xlf) ~ 1,
    TRUE ~ 0
  )) %>%
  group_by(file, age.rounded_s, avg_fr_s) %>%
  summarize(correct = mean(correct))

plot_model(xl_fr, type = "pred", terms = c("age.rounded_s","avg_fr_s")) +
  geom_point(data = trnsc.inc.indivs, inherit.aes = FALSE,
             aes(x = age.rounded_s, y = correct, color = factor(avg_fr_s))) +
  scale_color_manual(values = c("red", "orange", "green"),
                     labels = c("mean - 1sd", "mean", "mean + 1sd")) +
  scale_fill_manual(values = c("red", "orange", "green"),
                    guide = FALSE) +
  labs(color = "Avgerage\nfrequency\nscore",
       y = "% Correct", x = "Child age\n(standardized)") +
  theme_apa() +
  theme(plot.title = element_blank(),
        legend.key = element_rect(color = "white")) +
  guides(color = guide_legend(override.aes = list(fill = NA), reverse = TRUE))

<!-- ac2mc if it's easy for you to add dots representing actual children in the above, that would be awesome! If not, I can try to tackle it :)

mc2ac here's my attempt! i wasn't sure how you wanted to aggregate the real data to correspond to the model estimates so i have here grouped correctness within individual by
<= m - 1sd
mean <±> 1sd (unconventional notation, sorry)
>= m + 1sd

if you had something else in mind but are otherwise cool with the figure, it should be easy to edit on the mutate/case_when() portion defining trnsc.inc.indivs
-->
